\documentclass{article}
\thispagestyle{empty}
\usepackage{xcolor}
\usepackage[compact]{titlesec}
\usepackage{titling}
\usepackage[margin=.7in]{geometry}
\usepackage{setspace}
\usepackage[parfill]{parskip}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{letterspace}

\usepackage{microtype}

\titleformat{\section}
{\large\bfseries\uppercase}
{}
{0em}
{}[\titlerule]


\titleformat{\subsection}
{\bfseries}
{}
{0em}
{}

\titleformat{\subsubsection}[runin]
  {\bfseries}
  {}{0em}{}
  [\mbox{ -- }]

\renewcommand{\maketitle}{

\begin{center}
{\huge\bfseries
\theauthor}


aydenjmason@gmail.com --- aydenmason.com --- 618-979-2169
\end{center}
}

\setlist[itemize]{leftmargin=0em}

\begin{document}

\bgroup\obeylines
\title{Resume}
\author{Ayden Mason}

\maketitle
\color{blue}
\section{\\\textls[75]{Technologies and Languages}}
\color{black}
\begin{itemize}
\item Golang, C++, Python, JavaScript, Bash, pgSQL, DynamoDB, AWS
\item Docker, HTML, CSS, Git, Linux, API Design, Unit Testing
\end{itemize}
% uncomment for game dev jobs
%\subsubsection
%Unity, Blender, React
\color{blue}
\section{\\\textls[75]{Experience}}
\color{black}
\begin{itemize}
\subsection{\large Cigna\hfill\mdseries July 2021 - Present}
 \item[] \textit{Full-Stack Software Engineer } %[Golang, JavaScript, Python, Bash, Node.js]
\item Building middleware API layer for My.Cigna.com that offloads searching dynamoDB from a BFF layer to new middleware layer, yielding a more responsive app. Allows for other applications to utilize search functionalilty of dynamoDB. [Go]
\item Constructed automated tests for features before they were sent through CI/CD pipeline. [Go]
\item Successfully implemented features directly from headless archtiecure diagrams. [Go, API design]
\item Developed features for internal automation tool used for scheduling jobs and generating reports. Interfaced with customers, forlumated roadmapping,  provided analysis based on timelines. [JS, Node]
\item Designed an automated ETL process for survey responses that aggregates data from multiple sources. [Python, SQL]
\item Won enterprise-wide hackathon in 2022: Sentiment analysis on social media posts mentioning Cigna. [JS, Node]
\end{itemize}
\begin{itemize}
\subsection{\\\large Leidos\hfill\mdseries Summer 2019/2020}
\item[] \textit{Software Engineer Intern } %[JavaScript, SQL, VBA]
\item Acquired Department of Defense security clearance level: Secret.
\item Implemented security features required by DoD to be active on various webpages. [JS]
\item Researched new automation tool 'Itential' this application's purpose is to implement Software Defined Networking. Spent over half the summer gathering my findings. At the end of internship I presented my findings to upper managment and other important figures within the DoD.
\item Designed an org-chart generator. This chart was updated quarterly for criticial level stakeholders. [SQL, VBA]
\item Created an app that was paramount to senior staff members for time-sensitive, high-level roadmapping. [SQL, VBA]
\end{itemize}
\color{blue}
\section{\\\textls[75]{Education}}
\color{black}
\begin{itemize}
\subsection{\large Missouri University of Science and Technology\hfill\mdseries Graduated May 2021}
\item Bachelor of Science in Computer Science
\item Teaching Assistant for CS 5001 - Intro to Virtual Reality
\item ACM SIG COMP
\end{itemize}
\color{blue}
\section{\\\textls[75]{PROJECTS}}
\color{black}
\begin{itemize}
  \item 'eRolla' a marketplace web app that allows users in Rolla to sell items. [Python, Flask]
  \item Built a Lisp Interpeter. [C++]
  \item Currently building a Graphics Renderer to later be used for a game engine. [Go, C++]
  \end{itemize}
\end{document}